\chapter*{Abstract}
\addcontentsline{toc}{section}{Abstract}

Studies of the Milky Way show that the vertical velocity dispersion of
stars in the disk tends to increase with age. However it is not clear
how this ``heating'' ties into the formation of the observed Milky Way
disk structure, and disk galaxies in general. In this thesis I present
a study of stellar populations in NGC 891 that adds information to our
information on the structure of galaxies outside the Milky Way.

This study was enabled by the construction of HexPak/\GP, two fiber
integral field units that together form the worlds first dual-head,
multi-pitch fiber instrument. Specifically, the unique design of \GP
allowed for the rapid collection of high quality data over a large
range in surface brightness and at a high filling factor. 
% When designing HexPak/\GP I investigated sources of fiber focal
% ratio degredation and found that surface scattering likely plays a
% large role in the degredation of light emitted by fiber optics.

Using \GP I find that the overall picture of disk heating in NGC 891
is remarkably similar to trends measured in the Milky Way; the
presence of young populations is abruptly cut off at \asim 1 scale
height. Furthermore I find that populations generally get younger
farther from the center of NGC 891, which is perhaps the signature of
an inside-out formation scenario. It also appears that each generation
of stars forms a flared disk, with later generations forming flares at
larger radii.

Finally, I identify two distinct epochs in the enrichment history of
NGC 891: (i) a period of ``closed-box'' self-enrichment from galaxy
formation until \val{\asim 6.6}{Gyr} ago, and (ii) a period of
decreasing metallicity caused by the infall of pristine gas from
outside the galaxy that began \val{6.6}{Gyr} ago and continues today.
