\chapter*{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}

Humans cannot live on work alone, and without a good outlet for
frustration and pent up energy I would probably be on a lot more
governmental watchlists. Credit must first be given to Matt Bershady;
without your expert guidance and truly shocking (dangerous?)
willingness to listen to what I had to say none of this would have
been possible. You always pushed me just past my comfort zone and told
me \emph{what} to do, not \emph{how} to do it (until I did it wrong a
few times). The past six years rank extremely high in the epochs of my
development as a legit scientist, and I expect them to remain there
for a long time.

Beneath the Ivory Tower, in the beautiful slums of grad school, the
passage of time has been eased immeasurably by many of my fellow
travelers. To Andrew and Corey, thanks for being great research
partners. To Danielle and Britt, your feline obsession did little to
temper the pleasure of spending my first 2 years in your company. To
the Atom: Anna, Chris, Jenna, and John; thanks for giving me a couch
that I could use to get away from the cat talk. That and a lot of
snacks and scientific insight. Special mention is gladly given to
Jenna, who unwittingly accompanied me through the last 10 years. From
throwing lemons at East to biking to Michael's; it's been real. To
Diego, DK, Julie, and Max, the Young Blood that keeps me energized,
thanks for reducing the thickness of my jade layer with your youthful
enthusiasm and adorable 1st year problems. Me g\`usta. To Claire and
Elijah; sometimes a trip down the hall was all I needed and you
tolerated my interruptions with grace and good humor.

It would be impossible understate the importance of my family to my
apparent success. Unwavering support, unconditional love, and copious
amounts of Night Train are all crucial ingredients in the foundation
of this work.

To Mary, you have been with me through the thickest and the thinnest
and for that I will be forever grateful. You drive me to be the person
you think I am and are always willing to forgive my failings.

To Anna, the best student I ever had, your steadfast determination to
move forward despite fear and uncertainty is a continuing inspiration.

Thank you so much to The Begowatts, members past and present; you gave
me an outlet for the squishier parts of my brain and something to do
when I just wanted to hit something.

A very special thanks to the City Bar for being a refuge from the
storm. Kevin and MJ, you are the best bartenders I've ever had the
privilege to buy beer from; thanks for providing a welcoming
environment and slinging some wicked suds.

And finally, without music to dull the baser parts of my psyche none
of this would have happened. In the end recognition must be given to
The Boss for reminding me that being earnest can be cool, The Band
for so much joy (and especially ``Ophelia''),
NRW\footnote{\url{https://www.youtube.com/channel/UCAZ77vdqYbuGbCAWB62WbqQ}}
for a great background, and B{\"O}C for being with me from the
beginning.
