\defcitealias{Eigenbrot16b}{Paper 2}
\defcitealias{Eigenbrot16a}{Paper 1}
\defcitealias{Mosby15}{M15}
\defcitealias{Bruzual03}{BC03}
\defcitealias{Maraston11}{MA11}

\chapter[NGC 891: Full Spectrum Analysis]{Vertical Population Gradients in NGC 891 II. Spectral Analysis}
\label{chap:891_2}
\epigraph{\fixspacing\emph{Science is magic that \underline{works}}}{Kurt Vonnegut}
\vfill
\begin{flushright}
  \fixspacing
  \textit{A version of this chapter is currently in \\
    preparation to for submission to \apj}
\end{flushright}
\vspace{1in}
\cleardoublepage

\begin{chabstract}

  We report the results of applying full-spectrum fitting methods to
  IFU data from NGC 891. The edge-on nature of NGC 891 allows us to
  use line centroid velocity measurements to deproject on-sky radii
  and get a fully 3D picture of the location of our data in this
  galaxy. Our data are fit using a set of only 4 SSPs chosen, through
  statistical methods, to be a basis set for much larger SSP
  libraries. We attempt to refine the standard $\chi^2$ metric to make
  it more sensitive to spectral regions that encode information about
  age and metallicity, but find that this greatly increases
  uncertainty in our fits. Full spectral fits produce measurements of
  age, metallicity, and extinction as a function of height and radius
  in NGC 891. Examining trends in this phase space we determine that
  the disk of NGC 891 formed inside-out as a superposition of
  mono-aged flared disks (i.e., each subsequent disk flares at a
  larger radii). We also identify two distinct epochs in the
  enrichment history of the disk: before \val{6}{Gyr} ago the
  metallicity content of the galaxy increased with time, but since
  \val{6}{Gyr} the metallicity has been decreasing, likely an
  indication that pristine gas is currently infalling onto the disk of
  NGC 891.We are also able to make rough estimates about the star
  formation history of NGC 891.

% We have determined the vertical population gradients in age and
% metallicity in the disk of NGC 891 based on optical spectroscopy.
% These gradients, measured over a range of projected radii, are
% combined with estimates of the dust attenuation as a function of
% radius and height. Using a parameterization of the radial population 
% gradients in the disk plane, we model the heating rate in this spiral
% disk and compare it to estimates in the Milky Way solar neighborhood.
% This abstract will get augmented as we consolidate our results and
% make decisions about how we undertake the analysis and what object to
% include. Here and in the following manuscript outline the text gives a
% description of possible content and analysis choices.  These should be
% viewed as suggestions to be edited and commented out or deleted as
% items are completed.


\end{chabstract}

\input{891_2/introduction2}

\input{891_2/data2}

\input{891_2/basic_anal}

\input{891_2/LOS}

\input{891_2/SSP}

\input{891_2/chisq}

\input{891_2/SSP_err}

\input{891_2/results2}

\input{891_2/conclusion2}

\acknowledgements{We would like to thank Greg Mosby for making his
  diffusion k-means work available to us and answering our numerous
  question. Discussions with Marsha Wolf inspired many of the
  techniques used above. This research was directly supported by the
  U.S. National Science Foundation (NSF) AST-1517006.}

\bibliographystyle{thesis}
\bibliography{ms_n891_paper}

