%% \newcommand{\aeff}{{\rm A}_{\lambda}^{\rm e}}
%% \newcommand{\aej}{{\rm A}_{\rm J}^{\rm e}}
%% \newcommand{\aeh}{{\rm A}_{\rm H}^{\rm e}}
%% \newcommand{\aeks}{{\rm A}_{\rm K_{\rm s}}^{\rm e}}
%% \newcommand{\ks}{{K_{\rm s}}}
%% \newcommand{\GP}{$\nabla$Pak\xspace}
%% \newcommand{\Ha}{\ensuremath{\mathrm{H}\alpha}\xspace}
%% \newcommand{\HB}{\ensuremath{\mathrm{H}\beta}\xspace}
%% \newcommand{\Hd}{\ensuremath{\mathrm{H}\delta}\xspace}
%% \newcommand{\Hda}{\ensuremath{\mathrm{H}\delta_A}\xspace}
%% \newcommand{\Hg}{\ensuremath{\mathrm{H}\gamma}\xspace}
%% \newcommand{\He}{\ensuremath{\mathrm{H}\epsilon}\xspace}
%% \newcommand{\Zsol}{\ensuremath{Z_{\odot}}\xspace}
%% \newcommand{\tauV}{\ensuremath{\tau_{\mathrm{V,cont}}}\xspace}
%% \newcommand{\tauVB}{\ensuremath{\tau_{\mathrm{V,Balmer}}}\xspace}
%% \newcommand{\asim}{\ensuremath{{\sim}}}
%% %\documentclass[12pt,preprint]{aastex}
%% \documentclass[twocolumn,revtex4]{emulateapj}
%% %\usepackage[FIGTOPCAP]{subfigure}
%% \usepackage{subfigure}
%% %% \usepackage{caption}
%% %% \usepackage{subcaption}
%% \usepackage{upgreek}
%% \usepackage{amsmath}
%% \usepackage{xspace}
%% % \usepackage[page]{appendix}
%% \usepackage{appendix}
%% \usepackage{pdflscape}
%% % \usepackage{rotating}
%% \usepackage{multirow}
%% \usepackage{hyperref}

%% \newcommand{\val}[2]{\ensuremath{#1~\mathrm{#2} \xspace}}
%% \newcommand{\sol}[1]{\ensuremath{#1_{\odot} \xspace}}

%% \bibliographystyle{apj}
\defcitealias{Eigenbrot16a}{Paper 1}

\chapter[NGC 891: Observations and spectral data]{Vertical Population
  Gradients in NGC 891 I. Instrumentation and Spectral Data}
\label{chap:891_1}
\epigraph{\fixspacing\emph{If you save your breath I feel a man like you can manage it.}}{Tuco}

\vfill
\begin{flushright}
  \fixspacing
  \textit{A version of this chapter, with elements from Chapter \ref{chap:intro}\\
    is currently in preparation to for submission to \apj}
\end{flushright}
\vspace{1in}
\cleardoublepage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{chabstract}

  We have undertaken a study of the vertical and radial stellar
  population gradients in the edge-on spiral galaxy NGC 891. We
  compare gradients measured in integrated star-light to those known
  for the Milky Way disk from studies of resolved stars.  Our optical
  spectroscopic measurements between 3850 and \val{6850}{\AA} extend
  spatially from the disk midplane up to 2.6 kpc in height and out to
  a radius of 12 kpc on both the receding and approaching sides of the
  galaxy. Data were acquired with \GP, a variable-pitch fiber integral
  field unit (IFU) on the WIYN telescope designed specifically to
  sample vertical gradients in edge-on galaxies. We describe the
  laboratory and on-sky performance of \GP as well as modifications to
  the standard observational and analysis procedures to calibrate data
  taken with this unique IFU. The IFU itself has a mean throughput of
  80\% at \val{5500}{\AA}. To achieve an estimated precision of 10\%
  in light-weighted mean age and metallicity, we define a set of
  spatial apertures in radius and height in which spectra are binned
  to achieve a signal to noise of $\asim 20$ \AA$^{-1}$. We use
  spectral indices to measure age, metallicity, and
  abundance. Metallicities are found to be in the range from 0.2 to
  2.5 \Zsol, with abundances between solar and +0.3 dex. Metallicity
  and abundance gradients prove difficult to measure from indices
  alone for stellar populations with a broad range of ages. However,
  we find a clear transition from young ($<3 - \val{5}{Gyr}$) to old
  ($>\val{7}{Gyr}$) stellar populations at \val{0.4}{kpc}, roughly the
  scale height of the thin disk. We also find a slight trend towards
  younger populations at larger radii, consistent with an inside-out
  disk formation scenario.  The vertical age gradient in NGC 891 is in
  remarkable qualitative agreement with a model for disk heating tuned
  to studies of the Milk Way's solar cylinder.

% We have determined the vertical population gradients in age and
% metallicity in the disk of NGC 891 based on optical spectroscopy.
% These gradients, measured over a range of projected radii, are
% combined with estimates of the dust attenuation as a function of
% radius and height. Using a parameterization of the radial population 
% gradients in the disk plane, we model the heating rate in this spiral
% disk and compare it to estimates in the Milky Way solar neighborhood.
% This abstract will get augmented as we consolidate our results and
% make decisions about how we undertake the analysis and what object to
% include. Here and in the following manuscript outline the text gives a
% description of possible content and analysis choices.  These should be
% viewed as suggestions to be edited and commented out or deleted as
% items are completed.

\end{chabstract}
\cleardoublepage

\input{891_1/introduction1}

\input{891_1/gradpak}

\input{891_1/obs}

\input{891_1/redux}

\input{891_1/maps}

\input{891_1/results1}

\input{891_1/conclusion1}

\acknowledgements{We thank Guy Worthey for contributing his models of
  simple stellar populations as a function of age, metallicity and
  abundance. We thank Eric Hooper, as Interim WIYN Director, and
  Charles Corson for helping make the \GP installation possible; gift
  funds from the Department of Astronomy made this shipping and travel
  possible. This research was directly supported by the U.S. National
  Science Foundation (NSF) ATI-0804576, AST-1009471 and
  AST-1517006.}

\bibliographystyle{thesis}
\bibliography{ms_n891_paper}
